SDR enhancement by clouds

### 2024-03-07 article/article.Rmd
Commit 2024-03-07 20:18

```{r setup, echo=F, include=FALSE}
rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                               strip.white = TRUE,
                               sep = ";",
                               header = TRUE))
# ## create local citations file and links here
# source("~/CODE/FUNCTIONS/R/gather_citations.R")
# suppressMessages(
#     gather_citations(
#         sourcefile   = "./Article.Rmd",
#         mainreposit  = "./Mainreferences.bib",
#         localreposit = "./references.bib",
#         folderlink   = "./References_links",
#         workingdir   = "./"
#     )
# )
```

@@

@@

@@

.......

@@

-   some others were tested

We used as reference a modelled clear sky approximation,

criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}

\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
\end{cases}\label{eq:CE4}
\end{equation}
where: ..........

expand: libradtran calculations and modeling

@@

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data for AOD and water column from AERONET [@Giles2019; @Buis1998]. Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA [@Coddington2005] and Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
We have simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986]. 
We used the solar spectra of

- Kurudz wavelength
- solver

After some evaluation of the modelled conditions, in relation to the GHI data, we choose as more representative of the clear sky radiation, the case with $t_{500} - 1\sigma$ and $wc - 1\sigma$.

Lookup table creation ......

## Thresholds

@@

For some of this edge cases we further use images from a skycam, in order to evaluate our selection of the thresholds.

Thresholds by inspecting a selection of days with some specs

Reasoning for the selection

Include Example of days plot?

@@

@@

## Extrene CE above TSI

@@

## New plots for discusion

>>>>

```{r setup, echo=F, include=FALSE}
rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                               strip.white = TRUE,
                               sep = ";",
                               header = TRUE))
```

@@

CE and ECE usefulness

Identify CE cases

Characteristics of CE

Climatology and impact on the GHI

Effects of clouds

- enhancement physics
- conditions
- other interferences

....identification methods from bib....

- clearness index
- modeled approaches
- algorithmic id
- AI
- Visual

.....constrains of the site.....

- data
- instrument
- location

@@

- measured data
- available data
  - sky cam
  - chp1
  - cm21
  - cimel
- CSid tool

@@

..  todo ...

@@

@@

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data for AOD and water column from AERONET [@Giles2019; @Buis1998]. Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA [@Coddington2005] and Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
We have simulated the solar radiation spectrum of @Kurucz1994 in the range $280$ to $2500\,\text{nm}$, on $0.2^\circ$ SZA's step. 
With combinations of AOD at $500\,\text{nm}$ ($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column ($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].

<!-- - rte_solver  disort -->
<!-- - geometry   pseudospherical -->
<!-- - mol_abs LOWTRAN -->

After some evaluation of the modelled radiation in different atmospheric conditions, in relation to the GHI data, we choose as representative of the clear sky radiation, the case with $t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.

For each GHI measurement in our data we calculated a reference clear sky value, by adjusting the integral of the Kurudz spectrum to the interpolated TSI from NOAA. We applied the effect of Sun - Earth distance, and calculated it's value to the horizontal plane by using the cosine of the corresponding interpolated SZA. 
For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
Thus, we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.

## Thresholds investigation

@@

For some of this edge cases we further use images from a sky-cam, in order to evaluate our selection of the thresholds.

Thresholds by inspecting a selection of days with some specs......

Reasoning for the selection...........

We used as reference a modeled clear sky approximation,

Criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}

\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: $\theta$ solar zenith angle.

Include Example of days plot? Appendix?

@@

-   some other criteria were tested

@@

## Extreme CE above TSI

@@

## New plots for discussion
